---
title: "Casestudy1"
output:
 
  html_document: default
---

#2. Merge beer data with the breweries data. Print the first 6 observations and the last six observations to check the merged file.
```{r}
beers <- read.csv(file="/Users/afreensiddiqui/myhome/SMU/R/MSDS6306/afreenRwork/CaseStudy1files/Beers.csv", header=TRUE, sep=",")
breweries <- read.csv(file="/Users/afreensiddiqui/myhome/SMU/R/MSDS6306/afreenRwork/CaseStudy1files/Breweries.csv", header=TRUE, sep=",")
beersnbrew <- merge(beers, breweries, by.x=c("Brewery_id"), by.y = c("Brew_ID"), all=FALSE)
head(beersnbrew)
tail(beersnbrew)

```

#3. Report the number of NA's in each column
```{r}
colSums(is.na(beersnbrew))
```

#4.Compute the median alcohol content and international bitterness unit for each state. Plot a bar chart to compare.
```{r}
med.ABV<-tapply(beersnbrew$ABV, beersnbrew$State, median)
med.IBU<-tapply(beersnbrew$IBU, beersnbrew$State, median)
barplot(med.ABV, xlab="State", ylab="Median Alcoholic content", main ="Statewise Alcoholic flavour")
barplot(med.IBU, xlab="State", ylab="Median Alcohol Bitterness", main ="Statewise Alcohol Bitterness")
```

#5. Which state has the maximum alcoholic (ABV) beer? Which state has the most bitter (IBU) beer?
```{r}
maxABV <- beersnbrew[which.max(beersnbrew$ABV), ]
maxABVState<-levels(droplevels(maxABV$State))
print("State with maximum alcoholic (ABV) beer ")
maxABVState

maxIBU <- beersnbrew[which.max(beersnbrew$IBU), ]
maxIBUState<-levels(droplevels(maxIBU$State))
print("State with the most bitter (IBU) beer ")
maxIBUState

```

#6.Summary statistics for the ABV varia
```{r}
summary(beersnbrew$ABV)
```

#7.Is there an apparent relationship between the bitterness of the beer and its alcoholic content? Draw a scatter plot.
```{r}
beersnbrew[is.na(beersnbrew)] <- 0

library(ggplot2)
ggplot(beersnbrew, aes(x=IBU, y=ABV)) +
geom_point(shape=18, color="blue")+
geom_smooth(method=lm, se=FALSE, linetype="dashed",
color="darkred")
```

##If the data points make a straight line going from the origin out to high x- and y-values, then the variables are said to have a positive correlation .
#If the line goes from a high-value on the y-axis down to a high-value on the x-axis, the variables have a negative correlation .
# The figure, seems to be a fuzzy linear correlation so we will use Correlation Coefficient in order to measure of the linear dependence between IBU and ABV.
#The result will be a value between +1 and −1 inclusive, where 1 is total positive linear correlation, 0 is no linear correlation, and −1 is total negative linear correlation.
```{r}
cc <- cor(beersnbrew$ABV, beersnbrew$IBU)
cc
```

# the r value we got is 0.4 showing the slight positive corealtion between the IBU ans ABV that the alcoholic content may effect to the flavour
#or bitterness of alcohol.






